\begin{theorem}
 The satisfiability problem for $\PLTLA(\adomain)$ is \tower-hard.
\end{theorem}

\begin{proof}
Hardness follows from hardness from~\Cref{sec:prop-assign}.

    % \bigraul{The question is, can we reduce it into $\PLTLA(\adomain)$ with only 1 variable??}
\end{proof}

\subsection{Detour: A new decidable \FOL fragment over multi-data words} 

We need to introduce a new logic \defstyle{local \FOL over multi-data words}. Let $\{f_1,\dots,f_\beta\}$ be a set of function symbols:
\[
\begin{array}{l@{\;}l}
    \aformula, \aformulabis ::= & \avar = \avarbis \mid \avar < \avarbis \mid \avar = \avarbis + 1 \mid a(\avar) \mid \neg\aformula \mid \aformula \vee \aformulabis \\ 
    & \mid \exists x.\varphi \mid f_i(\avar + k_1) \sim f_j(\avar+k_2) \mid f_i(\avar + k_1) < f_j(\avar+k_2) \mid f_i(\avar + k_1) = a
\end{array}
\]

Models are of the form $(\adomain^\beta)^\omega$, and we call them multi-data words. \raul{This is just a sketch of the defs. We need to polish them}

\begin{theorem}
 The satisfiability problem for local \FOL over multi-data words is in \tower.
\end{theorem}

\begin{proof}
Lower bound follows from \tower-completeness of \FOL. \raul{Reference?}. Upper bound to check satisfiability of $\aformula$: 
\begin{enumerate}
    \item Use the notion of transfer graphs to characterize a window of comparison.
    \item Reduce the satisfiability problem into satisfiability over symbolic models (each letter of the path is a set of constraints over the variables involved).
    \item It remains to extract a concrete model from the symbolic model. This is performed due to \cite{Demri&Quaas2023}, by using the B\"chi automata $\mathbb{A}_\aformula$.
    \bigraul{Some missing step?}
\end{enumerate}
\end{proof}

\begin{conjecture}
    There is a translation from $\PLTLA(\adomain)$ into `local' $\FOL$ over multi-data words. Thus, the satisfiability problem for $\PLTLA(\adomain)$ is in \tower.
\end{conjecture}
